---
output:
  md_document:
    variant: markdown_github
---


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

tcadr
==============

[![Build Status](https://travis-ci.org/pbsag/tcadr.svg?branch=master)](https://travis-ci.org/pbsag/tcadr)

This is a library of functions that can be used to read native TransCAD files
directly into R without intermediate conversion to `.csv` or `.dbf`. Currently 
the package will read and write binary data tables (including network
attributes), but I hope to extend the package to cover shape data and networks
in the future.

Installation
--------------
The package is not (yet) on CRAN. The easiest way to install the latest stable
version is with

```r
devtools::install_github("pbsag/tcadr")
```
    
Using the [devtools](https://github.com/hadley/devtools) library may require you
to install `RTools` and `Rccp`, among other things.  

Use
--------------

```{r example}
library(tcadr)
dir("inst/extdata")
read_tcad("inst/extdata/TransitR.bin")


```


This package is under active development, and any contribution is welcome.

